Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-12 Grassmannian_cells.tex
Changed to \cH

Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$.
Write $\Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
Some results below remain true if we allow $H_m$ or $0$ as elements of $\Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.

For each $m\ge2$, there is an Auslander-Reiten sequence (cf.\ \cite[Section V]{ars})
\begin{equation}
  \label{eq:AR sequence}
  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
\end{equation}
where the right-hand morphism is the natural evaluation map.
\begin{lemma}
  \label{le:injective evaluation maps}
  For any $V\in \Gr(H_m)$, $m\geq 1$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
\begin{proof}
  As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
  \[\xymatrix{0 \ar[r] & P_{m-1}\ar@{=}[d]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[dr]|(.7){\lrcorner} \ar[r]\ar[d]_{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[d] & 0 \ar[d]\\ 0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0}\]
  in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
  Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker(ev_V)=0$ for $m=1$ and thus $ev_V$ is injective in this case.

  In view of Remark~\ref{rem:reflection recursion}, it is enough for the case $m>1$ to show that the cokernel of $ev_V$ does not have a preinjective direct summand when $m=1$.
  Clearly the cokernel of $\mathrm{id}_{P_1}\otimes \iota_V$ is isomorphic to $P_1\otimes H_1/V$.
  Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps, note that the vertical maps below are surjective:
  \[\xymatrix{0 \ar[r]  & P_1\otimes H_1 \ar[d]\ar[r]^{ev} &P_{2}\ar[d] \ar[r] & I_{1}\ar@{=}[d]\ar[r]&0\\ 0\ar[r] & P_1\otimes H_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0.}\]

  We need to show that $K$ has no preinjective direct summand.
  As $\Hom(P_2,P_1)=0$ and as the vertical maps are surjective, the representation $K$ has no direct summand which is isomorphic to $P_1=S_1$.
  But this already shows that $K$ is indecomposable as $\udim K=(\dim H_1/V,1)$.
  Since $V$ is a proper subspace of $H_1$, $\udim K$ is not the dimension vector of a preinjective representation and the claim follows.
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Truncated Preprojectives}
\label{sec:truncated preprojectives}
Motivated by Lemma~\ref{le:injective evaluation maps}, we define the following.
\begin{definition}
  For $V\in \Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
  \begin{equation}
    \label{eq:truncated preprojectives}
    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
  \end{equation}
\end{definition}
\begin{remark}
  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
\end{remark}

We collect below several basic homological results related to preprojective representations.
\begin{lemma}
  \label{le:truncated homomorphisms}
  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$ and $\Ext(P_m,P_{m+1}^V)=0$.
\end{lemma}
\begin{proof}
  As $P_m$ is exceptional, applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives}, gives an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}\]
  and an isomorphism
  \[\Ext(P_m,P_{m+1})\cong\Ext(P_m,P_{m+1}^V).\]
  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the first claim follows.
  The final claim follows from Theorem ~\ref{th:rigids} which implies $\Ext(P_m,P_{m+1})=0$.
\end{proof}

\begin{lemma}
  \label{le:unique preprojective morphism}
  For $V\in \Gr(H_m)$, $m\ge1$, the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
  Moreover, $\Ext(P_{m+1},P_{m+1}^V)=0$.
\end{lemma}
\begin{proof}
 As $\Hom(P_{m+1},P_m)=\Ext(P_{m+1},P_m)=0$, applying the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} gives isomorphisms 
  \[\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)\]
  and 
  \[\Ext(P_{m+1},P_{m+1})\cong\Ext(P_{m+1},P_{m+1}^V).\]
  Under the first isomorphism, the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
  The second isomorphism together with the rigidity of $P_{m+1}$ gives the final claim.
\end{proof}

\begin{lemma}
  \label{le:unique morphisms}
  Consider $V,W\in \Gr(H_m)$, $m\ge1$.
  \begin{enumerate}
    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
    \item For $W\subset V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(H_m/V)$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\longrightarrow 0.\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the morphism $-\circ ev_W$ of the above sequence is zero.
  But this occurs exactly when the image of the map $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$. 
  In this case, there are isomorphisms
  \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes H_m/V,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
\end{proof}
\begin{remark}
  The total Grassmannian $\Gr(H_m)$ is naturally a poset under inclusion.
  This structure gives rise to a $\CC$-linear category $\CC \Gr(H_m)$ with objects the elements of $\Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
  Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in \Gr(H_m)$.
  By Lemma~\ref{le:unique morphisms}(1), the functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC \Gr(H_m)\cong\cP_{m+1}$.
\end{remark}

For the truncated preprojective representations $P_{m+1}^V$, we have  $\udim P_{m+1}^V=d(m,\dim V):=\udim P_{m+1}-\dim V\cdot\udim P_m$.
These will play an important role when describing quiver Grassmannians of preprojective representations recursively.
For a dimension vector $d=(d_1,d_2)\in\NN^{K(n)_0}$, write 
\[R_d(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})\]
for the affine space of representations of $K(n)$ with dimension vector $d$. 
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
    \item The indecomposable representations of $K(n)$ with dimension vector $d(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(H_m)$ with $\dim V=r$. 
    \item The set of indecomposable representations with dimension vector $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(d(m,r))^\sigma=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $d(m,r)=(l,1)$ for $l:=n-r$.
  This means that $X\in R_{d(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=l-k$.

@@

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in\Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
\end{lemma}
\begin{proof}
  Recall that $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some indecomposable representation $X$ and some $\ell\ge1$ implies that $X$ is preprojective of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$).
  However, $P_{m+1}^V$ is indecomposable by Proposition~\ref{pro:indecomposables} and it cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
  %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
\end{proof}

\begin{lemma}
  \label{le:reflected truncated preprojectives}
  For $V\in\Gr(H_m)$, $m\ge2$, the representation $\Sigma_1(P_{m+1}^V)^\sigma$ is also truncated preprojective.
\end{lemma}
\begin{proof}
  By Proposition~\ref{pro:indecomposables} and Lemma~\ref{le:unique morphisms}, $P_{m+1}^V$ is indecomposable but not rigid.
  In particular, $P_{m+1}^V$ does not have a summand isomorphic to $S_1$.
  Thus, following Remark~\ref{rem:reflection recursion}, we may apply the functor $\Sigma_1(-)^\sigma$ to the sequence \eqref{eq:truncated preprojectives} to get the exact sequence
  \[0\longrightarrow P_{m-1}\otimes V\xrightarrow{\Sigma_1(ev_V)^\sigma} P_m\longrightarrow \Sigma_1(P_{m+1}^V)^\sigma\longrightarrow 0\]
  which gives the claim.
\end{proof}

\begin{lemma}
  \label{le:projective subrepresentations}
  For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
\end{lemma}
\begin{proof}
  We proceed by induction on $m$.
  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{H_m} V$.

@@

For $V\in \Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
\begin{corollary}
  \label{cor:base fibers}
  Consider $V,W\in \Gr(H_m)$, $m\ge1$, with $W\subset V$.
  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
\end{corollary}
\begin{proof}
  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and, since $X$ is a direct sum of preprojectives $P_r$ with $1\leq r\leq m$, the upper pullback sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  must split.
  The claim for arbitrary subrepresentations $Z\subset P_m\otimes(V/W)$ is an immediate consequence of this splitting.
\end{proof}

\begin{lemma}
  \label{le:unique truncated extension}
  For $V\in \Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
  \begin{equation}
    \label{eq:unique extension}
    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r]^(.625){ev} & P_{m+1}^V \ar[r] & 0}.
  \end{equation}
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
    & & 0 & 0 & }\]
  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
\end{proof}

>>>>

Set $\cH_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$.
Write $\Gr(\cH_m)$ for the \emph{total Grassmannian} of $\cH_m$ whose elements are nontrivial proper subspaces $V\subset \cH_m$.
Some results below remain true if we allow $\cH_m$ or $0$ as elements of $\Gr(\cH_m)$, but not all, so for uniformity of exposition we omit these possibilities.

For each $m\ge2$, there is an Auslander-Reiten sequence (cf.\ \cite[Section V]{ars})
\begin{equation}
  \label{eq:AR sequence}
  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes \cH_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
\end{equation}
where the right-hand morphism is the natural evaluation map.
\begin{lemma}
  \label{le:injective evaluation maps}
  For any $V\in \Gr(\cH_m)$, $m\geq 1$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
\begin{proof}
  As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
  \[\xymatrix{0 \ar[r] & P_{m-1}\ar@{=}[d]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[dr]|(.7){\lrcorner} \ar[r]\ar[d]_{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[d] & 0 \ar[d]\\ 0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes \cH_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0}\]
  in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
  Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker(ev_V)=0$ for $m=1$ and thus $ev_V$ is injective in this case.

  In view of Remark~\ref{rem:reflection recursion}, it is enough for the case $m>1$ to show that the cokernel of $ev_V$ does not have a preinjective direct summand when $m=1$.
  Clearly the cokernel of $\mathrm{id}_{P_1}\otimes \iota_V$ is isomorphic to $P_1\otimes \cH_1/V$.
  Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps, note that the vertical maps below are surjective:
  \[\xymatrix{0 \ar[r]  & P_1\otimes \cH_1 \ar[d]\ar[r]^{ev} &P_{2}\ar[d] \ar[r] & I_{1}\ar@{=}[d]\ar[r]&0\\ 0\ar[r] & P_1\otimes \cH_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0.}\]

  We need to show that $K$ has no preinjective direct summand.
  As $\Hom(P_2,P_1)=0$ and as the vertical maps are surjective, the representation $K$ has no direct summand which is isomorphic to $P_1=S_1$.
  But this already shows that $K$ is indecomposable as $\udim K=(\dim \cH_1/V,1)$.
  Since $V$ is a proper subspace of $\cH_1$, $\udim K$ is not the dimension vector of a preinjective representation and the claim follows.
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Truncated Preprojectives}
\label{sec:truncated preprojectives}
Motivated by Lemma~\ref{le:injective evaluation maps}, we define the following.
\begin{definition}
  For $V\in \Gr(\cH_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
  \begin{equation}
    \label{eq:truncated preprojectives}
    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
  \end{equation}
\end{definition}
\begin{remark}
  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
\end{remark}

We collect below several basic homological results related to preprojective representations.
\begin{lemma}
  \label{le:truncated homomorphisms}
  For $V\in \Gr(\cH_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong \cH_m/V$ and $\Ext(P_m,P_{m+1}^V)=0$.
\end{lemma}
\begin{proof}
  As $P_m$ is exceptional, applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives}, gives an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}\]
  and an isomorphism
  \[\Ext(P_m,P_{m+1})\cong\Ext(P_m,P_{m+1}^V).\]
  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the first claim follows.
  The final claim follows from Theorem ~\ref{th:rigids} which implies $\Ext(P_m,P_{m+1})=0$.
\end{proof}

\begin{lemma}
  \label{le:unique preprojective morphism}
  For $V\in \Gr(\cH_m)$, $m\ge1$, the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
  Moreover, $\Ext(P_{m+1},P_{m+1}^V)=0$.
\end{lemma}
\begin{proof}
 As $\Hom(P_{m+1},P_m)=\Ext(P_{m+1},P_m)=0$, applying the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} gives isomorphisms 
  \[\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)\]
  and 
  \[\Ext(P_{m+1},P_{m+1})\cong\Ext(P_{m+1},P_{m+1}^V).\]
  Under the first isomorphism, the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
  The second isomorphism together with the rigidity of $P_{m+1}$ gives the final claim.
\end{proof}

\begin{lemma}
  \label{le:unique morphisms}
  Consider $V,W\in \Gr(\cH_m)$, $m\ge1$.
  \begin{enumerate}
    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
    \item For $W\subset V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(\cH_m/V)$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\longrightarrow 0.\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the morphism $-\circ ev_W$ of the above sequence is zero.
  But this occurs exactly when the image of the map $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$. 
  In this case, there are isomorphisms
  \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes \cH_m/V,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
\end{proof}
\begin{remark}
  The total Grassmannian $\Gr(\cH_m)$ is naturally a poset under inclusion.
  This structure gives rise to a $\CC$-linear category $\CC \Gr(\cH_m)$ with objects the elements of $\Gr(\cH_m)$ and at most one morphism (up to scalars) between any two objects.
  Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in \Gr(\cH_m)$.
  By Lemma~\ref{le:unique morphisms}(1), the functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC \Gr(\cH_m)\cong\cP_{m+1}$.
\end{remark}

For the truncated preprojective representations $P_{m+1}^V$, we have  $\udim P_{m+1}^V=d(m,\dim V):=\udim P_{m+1}-\dim V\cdot\udim P_m$.
These will play an important role when describing quiver Grassmannians of preprojective representations recursively.
For a dimension vector $d=(d_1,d_2)\in\NN^{K(n)_0}$, write 
\[R_d(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})\]
for the affine space of representations of $K(n)$ with dimension vector $d$. 
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
    \item The indecomposable representations of $K(n)$ with dimension vector $d(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(\cH_m)$ with $\dim V=r$. 
    \item The set of indecomposable representations with dimension vector $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(d(m,r))^\sigma=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $d(m,r)=(l,1)$ for $l:=n-r$.
  This means that $X\in R_{d(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=l-k$.

@@

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in\Gr(\cH_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
\end{lemma}
\begin{proof}
  Recall that $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some indecomposable representation $X$ and some $\ell\ge1$ implies that $X$ is preprojective of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$).
  However, $P_{m+1}^V$ is indecomposable by Proposition~\ref{pro:indecomposables} and it cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
  %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
\end{proof}

\begin{lemma}
  \label{le:reflected truncated preprojectives}
  For $V\in\Gr(\cH_m)$, $m\ge2$, the representation $\Sigma_1(P_{m+1}^V)^\sigma$ is also truncated preprojective.
\end{lemma}
\begin{proof}
  By Proposition~\ref{pro:indecomposables} and Lemma~\ref{le:unique morphisms}, $P_{m+1}^V$ is indecomposable but not rigid.
  In particular, $P_{m+1}^V$ does not have a summand isomorphic to $S_1$.
  Thus, following Remark~\ref{rem:reflection recursion}, we may apply the functor $\Sigma_1(-)^\sigma$ to the sequence \eqref{eq:truncated preprojectives} to get the exact sequence
  \[0\longrightarrow P_{m-1}\otimes V\xrightarrow{\Sigma_1(ev_V)^\sigma} P_m\longrightarrow \Sigma_1(P_{m+1}^V)^\sigma\longrightarrow 0\]
  which gives the claim.
\end{proof}

\begin{lemma}
  \label{le:projective subrepresentations}
  For $V\in \Gr(\cH_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
\end{lemma}
\begin{proof}
  We proceed by induction on $m$.
  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.

@@

For $V\in \Gr(\cH_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
\begin{corollary}
  \label{cor:base fibers}
  Consider $V,W\in \Gr(\cH_m)$, $m\ge1$, with $W\subset V$.
  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
\end{corollary}
\begin{proof}
  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and, since $X$ is a direct sum of preprojectives $P_r$ with $1\leq r\leq m$, the upper pullback sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  must split.
  The claim for arbitrary subrepresentations $Z\subset P_m\otimes(V/W)$ is an immediate consequence of this splitting.
\end{proof}

\begin{lemma}
  \label{le:unique truncated extension}
  For $V\in \Gr(\cH_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
  \begin{equation}
    \label{eq:unique extension}
    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(\cH_m/V) \ar[r]^(.625){ev} & P_{m+1}^V \ar[r] & 0}.
  \end{equation}
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes \cH_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
    & & 0 & 0 & }\]
  from which we immediately obtain the isomorphism $X\cong P_m\otimes(\cH_m/V)$.
\end{proof}
